Privacy-preserving service provisioning using distributed networks

### 2023-01-14 paper/access.tex
update diagram and protocol steps

\title{Anonymous provision of services via blockchain}
\author{\uppercase{Stanis\l{}aw Bara{\'n}ski} \authorrefmark{1},
\uppercase{Julian Szyma{\'n}ski\authorrefmark{1} } 
 }

@@

\begin{abstract}
Service providers like lawyers, laboratories, auditors, or banks, to provide services, require customers to submit data often associated with their personal information. This situation exposes customers to privacy risks. However, most service providers use personal information merely for logistic operations like payments and communication and could provide services anonymously if other means of logistics exist.
We propose a protocol for coordinating anonymous service provision. Our proposal uses blockchain for both anonymous payments and proofs of existence (so-called message board) and content-addressable network (e.g.~IPFS) for results delivery.
A service provider can employ our protocol to provide services without collecting personal information. 
Possible applications for this protocol include anonymous tests for drugs, venereal diseases, paternity, and steroids, or anonymous legal advice.
In case of dispute, either due to exceeding deadlines or providing incorrect results, the customer can disclose the whole interaction and prove to justice (police or court) the misbehaviour of the service provider.
We provide the fairness analysis, implementation of the protocol, and discuss further extensions to an anonymous delivery system, and a decentralized conflict resolution system.
Our protocol may enable various services currently based on unacceptable trust assumptions to the service providers.
\end{abstract}

@@

By exposing our identity to the lawyer, we trust that he will not use that
information for harmful actions.

@@

%\paragraph{Organisation}
The remainder of this paper is organized as follows.
In section~\ref{sec:related-works} we briefly review related works. 
Section~\ref{sec:building-blocks} explains the building blocks of fair exchanges, blockchain, storage network, anonymity and confidentiality.
Section~\ref{sec:protocol} describes how the protocol works in detail.
Section~\ref{sec:fairness-analysis} provides a fairness analysis of the proposed protocol.
Section~\ref{sec:discussion} discuss possible improvements. 
Finally, section~\ref{sec:conclusion} concludes the paper.

@@

The most common application of anonymous fair exchange protocols is e-commerce.
The problem gets even more challenging when physical products are involved.
Authors of~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} proposed a protocol for fair exchange of physical products and electronic payments, which guarantee both customer and merchant anonymity. They achieve it by introducing online TTPs that validate coins and provide fair exchange guarantees.

@@

However, the protocol relies on strong assumptions to achieve fairness.
Namely,

\begin{itemize}
    \item there exists trusted third party (TTP) which does not misbehave or collude with any party;
    \item the customer's and merchant's banks enable confidential transactions, and both share commit-buffer where the value is locked until the transaction is finished;
    \item all banks maintain a global list of coins' serial numbers to prevent double-spending problems;
    \item the SC and DC exist, and in both, the product access is protected by a password;
    \item the DC is equipped with a video camera that records the moment when the customer opens the package and provides a way to submit the video to TTP in case of a dispute;
    \item there exists a trusted delivery agent;
    \item communication channels between parties provide anonymity.
\end{itemize}

@@

Our notion of anonymity is based on weaker (better) assumption. We achieve anonimity by using either cash or privacy-preserving blockchain. Moreover, our protocol does not require a customer to submit any transaction to the message board, which may be the weakest link in the anonymity of aforementioned protocols.

Our protocol does not handle the whole proces of delivery system (like courier). We assume that there is a mean to deliver the package securely and anonymously, either via trusted party.

Our protocol does not provide its own dispute resolution mechanism as Themis does. However, we assume the existence of an abstract justice, which can be instantiated with either local court or police, or one of the available online dispute resolution services like Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros, or others~\cite{allenGovernanceBlockchainDispute2019}.

@@

The vision of smart contracts was to replace the legal contract with
programmable and autonomous contracts. The smart contract code encompasses the contract's specifications, hence the slogan ``code as a law''.

@@

To mitigate the issue, we designed the protocol so that the SP who follows the protocol is always in an advantaged position; therefore, he has no reason to start a dispute. On the other hand, the customer can start a dispute at any time of the protocol, but only the actual misbehaviour of the SP makes him win the case.

@@

\subsection{Storage network}\label{storage-network}
Once the SP finishes its service, he has to provide the result to the customer. The most natural approach would be to send the result via e-mail or some dedicated platform. However, since the customer wants to stay anonymous, he does not want to expose his e-mail address nor IP address. Moreover, the SP should prove that the result has been provided before the deadline, which brings us to the issue of proof of existence discussed in section ~\ref{sec:message-board}.

@@

We take the same approach. Once the SP creates the result, he encrypts it using the previously provided encryption key and uploads it to the IPFS network.

@@

\item Anonymous payments: Monero \cite{vansaberhagenCryptoNote2013}, ZCash
  \cite{ben-sassonZerocashDecentralizedAnonymous2014}, Grin \cite{fuchsbauerAggregateCashSystems2019},
  Tornado Cash \cite{pertsevTornadoCashPrivacy2019}.
\item Message board: Stampery \cite{crespoStamperyBlockchainTimestamping2017}, Proof of Existence
  \cite{ProofExistenceOnline} (Bitcoin blockchain), Chainpoint
  \cite{ChainpointBlockchainProof} (Bitcoin blockchain), or any other blockchain that
  supports attaching extra data along the transaction.
\item Storage network: IPFS \cite{benetIPFSContentAddressed2014}, Filecoin
  \cite{protocollabsFilecoinDecentralizedStorage2017} (runs on top of IPFS), or Ethereum's
  Swarm\cite{teamSWARMStorageCommunication2021}.
\end{enumerate}

@@

$$\mathrm{PoD} \equiv (\mathrm{T}_\mathrm{issue}, \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide}, \mathrm{address}, \mathrm{provisionID}, \mathrm{pk(C)}, \mathrm{sig}_\mathrm{SP})$$

@@

\item $\mathrm{T}_\mathrm{issue}$ - time at which the $\mathrm{PoD}$ is issued.
\item
  $\mathrm{T}_\mathrm{pay}$ - deadline to pay for the transaction.
\item
  $\mathrm{T}_\mathrm{provide}$ - deadline to provide a result of the service.
\item $\mathrm{address}$ - payment address of the SP's anonymous blockchain account.
\item \(\mathrm{provisionID}\) - the number uniquely identifying the transaction previously generated by the customer.
\item $\mathrm{pk(C)}$ - customer's public key used to encrypt the result published on the public storage network.
\item $\mathrm{sig}_\mathrm{SP}$ - the SP's signature guaranteeing non-repudiation.
\end{itemize}

@@

The $\mathrm{PoP}$ is a digital construction published by the SP on the message board.

\[\mathrm{PoP} \equiv (\mathrm{cid}, \mathrm{nonce}, \mathrm{sig}_\mathrm{SP})\]

@@

The customer collects all the $\mathrm{materials}$ required by the SP, generates an encryption $\mathrm{key}$, prints it on a paper as a QR code, and packs them together into a package $\mathrm{pkg}$.

Symbolically: 
\[
\mathrm{pkg} \gets (\mathrm{materials}, \mathrm{key})
\]

@@

The protocol starts once the customer delivers package $\mathrm{pkg}$ and the SP accepts its content. In return, the SP issue a $\mathrm{PoD}$ with agreed upfront payment deadline $\mathrm{T}_\mathrm{pay}$, service provision deadline $\mathrm{T}_\mathrm{provide}$, and current time $\mathrm{T}_\mathrm{issue}$. Also, the $\mathrm{PoD}$ consist of randomly generated unique number $\mathrm{nonce}$, which will allow associating all actions related to the transaction throughout the protocol. Finally, the digital signature $\mathrm{sig}_{\mathrm{sk}(\mathrm{SP})}$ on the $\mathrm{PoD}$ created with the SP's secret key $\mathrm{sk}(\mathrm{SP})$ guarantee non-repudiation.

We assume this step to be entirely physical, i.e., $\mathrm{pkg}$ consists of physical materials, $\mathrm{PoD}$ is in the form of, e.g., QR code printed on a paper receipt.

$\mathrm{PoD}$ could be published on a message board (similarly to $\mathrm{PoP}$); however, since the $\mathrm{pkg}$ is delivered personally or via a trusted person, the confirmation can be issued in person. If we would like to hire a courier to deliver our $\mathrm{pkg}$, then the $\mathrm{PoD}$ would have to be published on the message board (further extension to the anonymous delivery system is discussed in section \ref{sec:discussion}).

Symbolically: 
\[
\mathrm{PoD} \gets \mathrm{delivery}(\mathrm{pkg})
\]
\[
(\mathrm{T}_\mathrm{issue}, \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide}, \mathrm{nonce}, \mathrm{sig}_{\mathrm{sk}(\mathrm{SP})}) \equiv \mathrm{PoD}
\]

\noindent \textbf
{Step 2. Payment}\label{step-2-payment}

Having the $\mathrm{PoD}$ issued, the SP can not reject receiving the package. At this point the
customer should pay for the transaction (identified by $\mathrm{nonce}$ value) with the agreed upfront cryptocurrency blockchain (see section~\ref{payment-for-services}).

@@

Symbolically: 
\[
\mathrm{attestation} \gets \mathrm{payment}(\mathrm{nonce}, \mathrm{sig}_{\mathrm{sk}(\mathrm{C})})
\]

\noindent \textbf
{Step 3. Provision of service}\label{step-3-provision-of-service} 
Once the customer has paid for the transaction, the SP starts providing the service.

Symbolically: 
\[
\mathrm{result} \gets \mathrm{provision}(\mathrm{materials})
\]

\noindent \textbf
{Step 4. Upload result }\label{step-4-results-upload}

After the service is finished, a result should be created. Next, the result is encrypted using encryption symmetric $\mathrm{key}$ provided in the first step.

The encrypted result is then uploaded on the content addressable network such as IPFS. In return the content identifier ($\mathrm{cid}$) is created.

Symbolically: 
\[
\mathrm{cid} \gets \mathrm{upload}(E_{\mathrm{key}}(\mathrm{result}))
\]

\noindent \textbf
{Step 5. Proof of provision}\label{step-5-proof-of-provision-publication}

When the result is published, the SP performs proof of provision by publishing $\mathrm{cid}$ along with $\mathrm{nonce}$ and signature $\mathrm{sig}_\mathrm{SP}$.

Symbolically: 
\[
\mathrm{PoP} \equiv (\mathrm{cid}, \mathrm{nonce}, \mathrm{sig}_{\mathrm{sk}(\mathrm{SP})})
\]
\[
\mathrm{publish}(\mathrm{PoP})
\]

\noindent \textbf
{Step 6. Pull proof of provision}\label{step-6-proof-of-provision-notification}

After delivering the package and paying for the transaction, the customer subscribes to the message board and waits until the SP publishes the proof of provision. The subscription is for the SP public key $\mathrm{pk}(\mathrm{SP})$ and transaction's $\mathrm{nonce}$.

Symbolically: 
\[
\mathrm{cid} \gets \mathrm{subscribe}(\mathrm{pk}(\mathrm{SP}), \mathrm{nonce})
\]

\noindent \textbf
{Step 7. Result download}\label{step-7-results-download} 
Having the $\mathrm{cid}$, the customer downloads and decrypts the $\mathrm{result}$.

Symbolically: 
\[
\mathrm{result} \gets \mathrm{D}_{\mathrm{key}}(\mathrm{download}(\mathrm{cid}))
\]
\section{Fairness analysis}\label{sec:fairness-analysis}

We analyze the fairness of the protocol by representing it as an interactive non-cooperative game.

\subsection{Model}\label{model}
We consider three positions:

@@

As a result, in our analysis, we have to consider four different outcomes for each party of the protocol ($\mathrm{party \in \{c, s}\}$), for each step of the protocol ($\mathrm{step \in 1..7}$):

@@

Because the customer is anonymous, the SP can not start a dispute—there is no means to identify the customer. To mitigate the issue, we designed the protocol so that the SP who follows the protocol is always in an advantaged position, and therefore he has no reason to start a dispute. On the other hand, the customer can start a dispute at any time of the protocol, but only the actual misbehaviour of the SP makes him win the case.

@@

The description of each step and the rationale of the outcome position is given in the appendix in section \ref{sec:proof-of-fairness}.

@@

  \item{monerod and monero-wallet-cli} — v0.18.1.2-release
  \item{Powergate} — v2.6.2-7-gfd1d093-dirty
  \item{Ganache} — v7.5.0
  \item{Solidity} — v0.8.17
  \item{ReactJS} — v18.0.25
  \item{web3.js} — v1.8.1
  \item{crypto-js} — v4.1.1
\end{itemize}

@@

  \item 4. Since (in this experiment) the provision has not been paid in cash, the SP generate unique Monero payment address using $\mathtt{monero-wallet-cli integrated_address}$ command, and submits the proof of delivery to the Ethereum blockchain.

  % monero-wallet-cli --stagenet --wallet-file sp --password "" integrated_address
  % Random payment ID: <2b6d65d7d48b7896>
  % Matching integrated address: 5LHmrsVsQM2Q2TgqufX4A5gKPpxy1czHULDyVc84omvnh1nQLVmqXk4VBuy8WnX1AXfKxDx7xuASAc6svkZqGVkL1XkUBWT7QejHymEaYM
  \item 5. The customer (using the webapp) check the transaction status on the Ethereum blockchain invoking $\mathtt{getProvision(customerPubKey, provisionID)}$.
  % monero-wallet-cli --stagenet --wallet-file customer --password "" transfer 5LHmrsVsQM2Q2TgqufX4A5gKPpxy1czHULDyVc84omvnh1nQLVmqXk4VBuy8WnX1AXfKxDx7xuASAc6svkZqGVkL1XkUBWT7QejHymEaYM 1
  % Transaction successfully submitted, transaction <7d89c04de458cfb76a811d5eb325075dec59f7a993c3bf7ce37f9e3a1630af65>
  % monero-wallet-cli --stagenet --wallet-file customer --password "" get_tx_key 7d89c04de458cfb76a811d5eb325075dec59f7a993c3bf7ce37f9e3a1630af65
  % Tx key: 1364dc848a752bf52011f4a63d98bcb16091cacd985713b6b5264b3ede6de40f

@@

The first approach is more feasible in the near future. It would require creating a large set of experts in a field that, in case of dispute, would receive all the proofs ($\mathrm{PoD}$, $\mathrm{PoP}$, payment $\mathrm{attestation}$ as well as any other proofs significant to the case) that could be queried by the experts in zero-knowledge fashion, i.e., they could ask a limited number of questions to the proofs and getting yes/no answers. The case would be fully confidential as they would not be able to query personal information. The experts would be incentivized to participate in the pool by the system of fees. They would be incentivized to vote honesty by the stake they would have to lock and reward/punishment they would get by judging correctly/incorrectly, where the ``correctly'' is determined by the quorum of votes.

@@

\section*{Appendix A: Proof of fairness}\label{sec:proof-of-fairness}
Below we describe each step and rationale of the outcome position.

@@

\begin{itemize}
\item Agreeable path:
  \begin{itemize}
  \item
    \(\operatorname{\sigma_{1, c, n} = \sbullet}\), the customer has risked its materials but has not paid anything, so we assume he is in the neutral position \footnote{One would argue that the customer has put effort into delivering the materials to the SP or that the sample is valuable. We assume that the sample without personal information is useless, and the effort to deliver the package is negligible.}.
  \item
    \(\operatorname{\sigma_{1, s, n} = \sbullet}\), the SP is in a neutral position as he did not put any effort, and the package has not brought any value to the SP.
  \end{itemize}
\item
  Starting a dispute:

@@

\item
  The customer can follow the protocol and move to the non-disadvantaged position \(\operatorname{\sigma_{1, c, n} = \sbullet}\).
\item
  The SP can do nothing and end up in the non-disadvantaged position \(\operatorname{\sigma_{1, s, n} = \sbullet}\) or \(\operatorname{\sigma_{1, s, d} = \sbullet}\).
\end{itemize}

\noindent \textbf
{Step 2. Customer turn: payment}\label{step-2-pay-for-invoice}

>>>>

\title{Privacy-preserving service provisioning using distributed networks}
\author{\uppercase{Stanis\l{}aw Bara{\'n}ski} \authorrefmark{1},
\uppercase{Julian Szyma{\'n}ski\authorrefmark{1} } 
 }

@@

\begin{abstract}
Service providers like lawyers, laboratories, auditors, or banks, to provide services, require customers to submit data often associated with their personal information, exposing their customers to privacy risks. However, most service providers use personal information merely for logistic operations like payments and communication and could provide services anonymously if other means of logistics exist.
We propose a anonymous fair exchange protocol for coordinating service provision using blockchain for both anonymous payments and proofs of existence and content-addressable network for results delivery.
% Less important
A service provider can employ our protocol to provide services without collecting personal information, enabling services currently based on unacceptable trust assumptions. 
% Even less important
Possible applications for this protocol include anonymous tests for drugs, venereal diseases, paternity, and steroids, or anonymous legal advice.
We provide the fairness analysis and well as the implementation of the protocol. We discuss further extensions to an anonymous delivery system, and a decentralized conflict resolution system.
\end{abstract}

@@

By exposing our identity we trust that the lawer will not use that information for harmful actions.

@@

%\paragraph{Organisation}
The remainder of this paper is organized as follows.
In section~\ref{sec:related-works} we review related works. 
Then, in section~\ref{sec:building-blocks} we explain the building blocks of fair exchanges, blockchain, storage network, anonymity and confidentiality.
Section~\ref{sec:protocol} describes how the protocol works in detail.
Section~\ref{sec:fairness-analysis} provides a fairness analysis of the proposed protocol.
Section~\ref{sec:discussion} discuss possible improvements. 
Finally, section~\ref{sec:conclusion} concludes the paper.

@@

The most common application of anonymous fair exchange protocols is e-commerce. The problem is that the customer wants to buy a product from a merchant, but does not want to reveal his identity to the merchant. The problem gets even more challenging when physical products are involved.

Authors of~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} proposed a protocol for fair exchange of physical products and electronic payments, which guarantee both customer and merchant anonymity. They achieve it by introducing online TTPs that validate coins and provide fair exchange guarantees.

@@

However, the protocol relies on strong assumptions, namely:

\begin{itemize}
    \item there exists trusted third party (TTP) and trusted delivery agent which do not misbehave or collude with any party;
    \item there exists an anonymous communication channel 
    \item the customer's and merchant's banks enable confidential transactions, and both share commit-buffer where the value is locked until the transaction is finished;
    \item all banks maintain a global list of coins' serial numbers to prevent double-spending problems;
    \item the SC and DC exist, and in both, the access is protected by a password;
    \item the DC is equipped with a video camera that records the moment when the customer opens the package and provides a way to submit the video to TTP in case of a dispute;
\end{itemize}

@@

Our protocol achieves stronger anonymity guarantees. Namely, we achieve anonimity by using either cash or privacy-preserving blockchains. Moreover, our protocol does not require a customer to submit any transaction to the message board, which may be the weakest link in the anonymity of aforementioned protocols.

Our protocol does not use its own delivery system. We assume that there is a way to anonymously deliver a package either via SP's drop box, or trusted party.

Also, our protocol does not provide its own dispute resolution mechanism as Themis does. However, we assume the existence of an abstract justice which accepts evidences and ., which can be instantiated with either local court or police, or one of the available online dispute resolution services like Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022}, Aragon Court\footnote{https://aragon.org/aragon-court}, or others~\cite{allenGovernanceBlockchainDispute2019}.

@@

The vision of smart contracts was to replace the legal contract with
programmable and autonomous contracts. The smart contract code encompasses the contract's specifications, hence the slogan \textit{code as a law}.

@@

To mitigate the issue, we designed the protocol so that the SP who follows the protocol is always in an advantaged position; therefore, she has no reason to start a dispute. On the other hand, the customer can start a dispute at any time of the protocol, but only the actual misbehaviour of the SP makes him win the case.

@@

\subsection{Storage network}\label{storage-network}
Once the SP finishes its service, she has to provide the result to the customer. The most natural approach would be to send the result via e-mail or some dedicated platform. However, since the customer wants to stay anonymous and so does not want to expose his e-mail address nor IP address. Moreover, the SP should prove that the result has been provided before the deadline, which brings us to the issue of proof of existence discussed in section ~\ref{sec:message-board}.

@@

We take the same approach. Once the SP creates the result, she encrypts it using the previously provided encryption key and uploads it to the IPFS network.
%TODO: write about DHKE encyption

@@

\item Anonymous payments: Monero \cite{vansaberhagenCryptoNote2013}, ZCash
  \cite{ben-sassonZerocashDecentralizedAnonymous2014}, Grin \cite{fuchsbauerAggregateCashSystems2019},
  Tornado Cash \cite{pertsevTornadoCashPrivacy2019}.
\item Message board: Stampery \cite{crespoStamperyBlockchainTimestamping2017}, Proof of Existence
  \cite{ProofExistenceOnline} (Bitcoin blockchain), Chainpoint
  \cite{ChainpointBlockchainProof} (Bitcoin blockchain), or any other blockchain that
  supports attaching extra data along the transaction.
\item Storage network: IPFS \cite{benetIPFSContentAddressed2014}, Filecoin
  \cite{protocollabsFilecoinDecentralizedStorage2017}, or Ethereum's
  Swarm\cite{teamSWARMStorageCommunication2021}.
\end{enumerate}

@@

\begin{eqnarray}
\mathrm{PoD} & \equiv & (\begin{array}[t]{l}\mathrm{T}_\mathrm{issue}, \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide},\\ \mathrm{address}, \mathrm{provisionID}, \mathrm{pk(C)}, \mathrm{sig}_\mathrm{SP} \; )\end{array}
\end{eqnarray}

% \begin{eqnarray}
%   \quad L_{\mathrm{H}}(H) & \equiv & (\begin{array}[t]{l}H_{\mathrm{p}}, H_{\mathrm{o}}, H_{\mathrm{c}}, H_{\mathrm{r}}, H_{\mathrm{t}}, H_{\mathrm{e}}, H_{\mathrm{b}}, H_{\mathrm{d}},\\ H_{\mathrm{i}}, H_{\mathrm{l}}, H_{\mathrm{g}}, H_{\mathrm{s}}, H_{\mathrm{x}}, H_{\mathrm{m}}, H_{\mathrm{n}} \; )\end{array} \\
%   \quad L_{\mathrm{B}}(B) & \equiv & \big( L_{\mathrm{H}}(B_{\mathrm{H}}), \widetilde{L}_{\mathrm{T}}^*(B_{\mathbf{T}}), L_{\mathrm{H}}^*(\hyperlink{ommer_block_headers_B__U}{B_{\mathbf{U}}}) \big)
%   \end{eqnarray}

@@

\item $\mathrm{T}_\mathrm{issue}$ - time at which the $\mathrm{PoD}$ is issued.
\item
  $\mathrm{T}_\mathrm{pay}$ - deadline to pay for the transaction.
\item
  $\mathrm{T}_\mathrm{provide}$ - deadline to provide a result of the service.
\item $\mathrm{address}$ - payment address of the SP's anonymous blockchain account.
\item $\mathrm{provisionID}$ - the number uniquely identifying the transaction previously generated by the customer.
\item $\mathrm{pk(C)}$ - customer's public key used to encrypt the result published on the public storage network.
\item $\mathrm{sig}_\mathrm{SP}$ - the SP's signature guaranteeing non-repudiation.
\end{itemize}

@@

$\mathrm{PoP}$ is published on the message board by the SP.

\begin{eqnarray}
\mathrm{PoP} & \equiv & (\mathrm{cid}, \mathrm{provisionID}, \mathrm{sig}_\mathrm{SP})
\end{eqnarray}

@@

The customer collects all the $\mathrm{materials}$ required by the SP, generates a random $\mathrm{provisionID}$ and a random keypair $(\mathrm{sk(C)},\mathrm{pk(C)})$. The $\mathrm{provisionID}$ will be used to associate all actions related to the transaction throughout the protocol. The $\mathrm{provisionID}$ and $\mathrm{pk(C)}$ are encoded as a QR code, printed, and sticked to the package $\mathrm{pkg}$. The $\mathrm{sk(C)}$ is kept secret and used to decrypt the $\mathrm{result}$ at the end of the protocol.

@@

The protocol starts once the customer delivers package $\mathrm{pkg}$ to the SP and its content gets accepted. As a result, $\mathrm{PoD}$ is created with predefined payment deadline $\mathrm{T}_\mathrm{pay}$, service provision deadline $\mathrm{T}_\mathrm{provide}$, and current time $\mathrm{T}_\mathrm{issue}$. Also $\mathrm{PoD}$ embodies the information whether the service has been paid in cash or should be paid by the customer using the anonymous blockchain account. In the latter case, the SP's payment address is included in the $\mathrm{PoD}$.

The digital signature $\mathrm{sig}_{\mathrm{sk}(\mathrm{SP})}$ on the $\mathrm{PoD}$ created with the SP's secret key $\mathrm{sk}(\mathrm{SP})$ guarantee non-repudiation.

Symbolically: 
\[
\mathrm{PoD \gets delivery(pkg)}
\]

\noindent \textbf
{Step 2. Proof of Delivery}\label{step-2-pod}

Then, the $\mathrm{PoD}$ is published on the message board by the SP, commiting to the fact that the package $\mathrm{pkg}$ has been delivered, adn the SP can not reject receiving it. If the provision has not been paid in cash, the SP waits for the customer to pay for the service on the specified in the $\mathrm{PoD}$ payment $\mathrm{address}$.

Symbolically: 
\[
\mathrm{publish(PoD)}
\]

\noindent \textbf
{Step 3. Get Proof of Delivery}\label{step-3-get-pod}

Once the package is delivered and the $\mathrm{PoD}$ is published, the customer can get the $\mathrm{PoD}$ from the message board and (if everything is correct) proceed with the protocol.

Symbolically: 
\[
\mathrm{PoD \gets get(provisionID)}
\]

\noindent \textbf
{Step 4. Payment}\label{step-4-payment}

If the provision has not been paid in cash, the customer should pay for the transaction with the predefined anonymous payment blockchain (see section~\ref{payment-for-services}).

@@

Symbolically: 
\[
\mathrm{attestation \gets payment(address)}
\]

\noindent \textbf
{Step 5. Provision of service}\label{step-5-provision-of-service} 
Once the customer has paid for the transaction either in cash or using the anonymous blockchain, the SP can start providing the service.

Symbolically: 
\[
\mathrm{result \gets provision(materials)}
\]

\noindent \textbf
{Step 6. Upload result}\label{step-6-upload-result}

After the service is finished, a result should be created. 
Next, the result is encrypted using shared key derived from the customer's public key $\mathrm{pk(C)}$ and the SP's secret key $\mathrm{sk(S)}$ using Diffie-Hellman key exchange (DHKE) method.

The encrypted result is then uploaded on the content addressable network (such as IPFS). In return the content identifier ($\mathrm{cid}$) is created.

Symbolically: 
\[
\mathrm{cid \gets upload(E_{DHKE(sk(SP), pk(C))}(result))}
\]

\noindent \textbf
{Step 7. Proof of provision}\label{step-7-proof-of-provision}

When the $\mathrm{result}$ is uploaded, the SP creates and publish on a message board a proof of provision consisting of $\mathrm{cid}$ along with $\mathrm{provisionID}$ and signature $\mathrm{sig}_\mathrm{SP}$.

Symbolically: 
\[
\mathrm{publish(PoP)}
\]

\noindent \textbf
{Step 8. Get Proof of Provision}\label{step-8-get-proof-of-provision}

After delivering the package and paying for the transaction, the customer start listening to the message board and waits until the SP publishes the $\mathrm{PoP}$ for the $\mathrm{provisionID}$.

Symbolically: 
\[
\mathrm{cid \gets get(provisionID)}
\]

\noindent \textbf
{Step 9. Download result}\label{step-9-download-result} 
Having the $\mathrm{cid}$, the customer downloads and decrypts the $\mathrm{result}$ using shared key derived from the customer's secret key $\mathrm{sk(C)}$ and the SP's public key $\mathrm{pk(S)}$ using DHKE method. The protocol ends.

Symbolically: 
\[
\mathrm{result \gets D_{DHKE(sk(C), pk(SP))}(download(cid))}
\]

\section{Fairness analysis}\label{sec:fairness-analysis}
We analyze the fairness of the protocol by representing it as an interactive non-cooperative game.

\subsection{Model}\label{sec:fairness-model}
We consider three positions:

@@

As a result, in our analysis, we have to consider four different outcomes for each party of the protocol ($\mathrm{party \in \{c, s}\}$), for each step of the protocol ($\mathrm{step \in 1..9}$):

@@

Because the customer is anonymous, the SP can not start a dispute—there is no means to identify the customer. To mitigate the issue, we designed the protocol so that the SP who follows the protocol is always in an advantaged position, and therefore has no reason to start a dispute. On the other hand, the customer can start a dispute at any time of the protocol, but only the actual misbehaviour of the SP makes him win the case.

@@

The description of each step and the rationale of the outcome position is given in the Appendix~\ref{app:proof-of-fairness}.

@@

  \item{monerod and monero-wallet-cli} — v0.18.1.2
  \item{Powergate} — v2.6.2
  \item{Ganache} — v7.5.0
  \item{Solidity} — v0.8.17
  \item{ReactJS} — v18.0.25
  \item{web3.js} — v1.8.1
  \item{crypto-js} — v4.1.1
\end{itemize}

@@

  \item 4. Since (in this experiment) the provision has not been paid in cash, the SP generate unique Monero payment address using \texttt{monero-wallet-cli integrated\_address} command, and submits the proof of delivery to the Ethereum blockchain.

  % monero-wallet-cli --stagenet --wallet-file sp --password "" integrated_address
  % Random payment ID: <2b6d65d7d48b7896>
  % Matching integrated address: 5LHmrsVsQM2Q2TgqufX4A5gKPpxy1czHULDyVc84omvnh1nQLVmqXk4VBuy8WnX1AXfKxDx7xuASAc6svkZqGVkL1XkUBWT7QejHymEaYM
  \item 5. The customer (using the webapp) check the transaction status on the Ethereum blockchain invoking \texttt{getProvision(customerPubKey, provisionID)}.
  % monero-wallet-cli --stagenet --wallet-file customer --password "" transfer 5LHmrsVsQM2Q2TgqufX4A5gKPpxy1czHULDyVc84omvnh1nQLVmqXk4VBuy8WnX1AXfKxDx7xuASAc6svkZqGVkL1XkUBWT7QejHymEaYM 1
  % Transaction successfully submitted, transaction <7d89c04de458cfb76a811d5eb325075dec59f7a993c3bf7ce37f9e3a1630af65>
  % monero-wallet-cli --stagenet --wallet-file customer --password "" get_tx_key 7d89c04de458cfb76a811d5eb325075dec59f7a993c3bf7ce37f9e3a1630af65
  % Tx key: 1364dc848a752bf52011f4a63d98bcb16091cacd985713b6b5264b3ede6de40f

@@

The first approach is more feasible in the near future. It would require creating a large set of experts in a field that, in case of dispute, would receive all the proofs ($\mathrm{PoD}$, $\mathrm{PoP}$, payment $\mathrm{attestation}$ as well as any other proofs significant to the case) that could be queried by the experts in zero-knowledge fashion, i.e., they could ask a limited number of questions to the proofs and getting yes/no answers. The case would be fully confidential as they would not be able to query personal information. The experts would be incentivized to participate in the pool by the system of fees. They would be incentivized to vote honesty by the stake they would have to lock and reward/punishment they would get by judging correctly/incorrectly, where the correctness is determined by the quorum of votes.

@@

\appendices

\section{Appendix A: Proof of fairness}\label{app:proof-of-fairness}
Below we describe each step and rationale of the outcome position.
We use the notation intoruced in Section~\ref{sec:fairness-model} to analise each position in the protocol.

@@

\begin{itemize}
\item Agreeable path:
  \begin{itemize}
  \item
    \(\operatorname{\sigma_{1, c, n} = \sbullet}\), the customer has risked its materials but has not paid for the transaction, so we assume he is in the neutral position \footnote{One would argue that the customer has put effort into delivering the materials to the SP or that the sample is valuable. We assume that the sample without personal information is useless, and the effort to deliver the package is negligible.}.
  \item
    \(\operatorname{\sigma_{1, s, n} = \sbullet}\), the SP is in a neutral position as she did not put any effort, and the package has not brought any value to the SP.
  \end{itemize}
\item
  Starting a dispute:

@@

\item
  The customer can follow the protocol to the non-disadvantaged position \(\operatorname{\sigma_{1, c, n} = \sbullet}\).
\item
  The SP can do nothing and always ends up in the non-disadvantaged position.
\end{itemize}

\noindent \textbf
{Step 2. SP turn: proof of delivery}\label{step-2-proof-of-delivery}

The SP has published proof of delivery:

  \item
    \(\operatorname{\sigma_{2, c, n} = \sbullet}\), the customer remains in the neutral position as the PoD allows him to pay for the transaction but does not obligate him to anything.
  \item
    \(\operatorname{\sigma_{2, s, n} = \sbullet}\), the SP is in a neutral position as she did not put any effort to provide the service, and the package has not brought any value to the SP.
  \end{itemize}
\item
  Starting a dispute:

  \item
    \(\operatorname{\sigma_{2, c, d} = -}\), the customer loses the case as the SP didn't receive the payment on time.
  \item
    \(\operatorname{\sigma_{2, s, d} = \sbullet}\), the SP win the case for the same reason.
  \end{itemize}
\end{itemize}

  \item
    \(\operatorname{\sigma_{2, c, \overline{n}} = \sbullet}\), the customer remains in the neutral position as he is not obligated agree with the incorrect $\mathrm{PoD}$.
  \item
    \(\operatorname{\sigma_{2, s, \overline{n}} = \sbullet}\), the SP is in a neutral position as she did not put any effort to provide the service, and the package has not brought any value to the SP.
  \end{itemize}
\item
  Starting a dispute:

  \item
    \(\operatorname{\sigma_{2, c, \overline{d}} = -}\), the customer loses the case as the SP is not obligated to publish correct $\mathrm{PoD}$.
  \item
    \(\operatorname{\sigma_{2, s, \overline{d}} = \sbullet}\), the SP win the case for the same reason.
  \end{itemize}
\end{itemize}

\item The customer can do nothing and always ends up in a non-disadvantaged position.
\item The SP can follow the protocol ends up in the non-disadvantaged position \(\operatorname{\sigma_{2, s, n} = \sbullet}\).

\noindent \textbf
{Step 3. customer turn: get proof of delivery}\label{step-3-get-proof-of-delivery}

The customer has got the PoD, then:

  \item
    $\operatorname{\sigma_{3, c, n} = \sbullet}$, the customer has the opportunity to pay for the transaction, but since he didn't put any effort, he is in the neutral position.
  \item
    $\operatorname{\sigma_{3, s, n} = \sbullet}$, the SP position has not changed.
  \end{itemize}
\item
  Starts a dispute:

  \item
    $\operatorname{\sigma_{3, c, d} = -}$, the customer loses the case as the SP didn't receive the payment on time.
  \item
    $\operatorname{\sigma_{3, s, d} = \sbullet}$, the SP win the case for the same reason.
  \end{itemize}
\end{itemize}

  \item
    \(\operatorname{\sigma_{3, c, \overline{n}} = \sbullet}\), the customer can not follow the protocol but since he didn't put any efford he is in the neutral position.
  \item
    \(\operatorname{\sigma_{3, s, \overline{n}} = \sbullet}\), the SP position has not changed.
  \end{itemize}
\item
  Starts a dispute:

  \item
    \(\operatorname{\sigma_{3, c, \overline{d}} = -}\), the customer loses the case as the SP is not obligated to do anything before the payment is made.
  \item
    \(\operatorname{\sigma_{3, s, \overline{d}} = \sbullet}\), the SP wins the case and ends up in the neutral position.
  \end{itemize}
\end{itemize}

\item The customer can follow the protocol to the non-disadvantaged position \(\operatorname{\sigma_{3, c, n} = \sbullet}\).
\item The SP can do nothing and always ends up in a non-disadvantaged position.
\end{itemize}

\noindent \textbf
{Step 4. Customer turn: payment}
